The globular cluster system of the Auriga simulations

### 2019-08-20 AurigaGCS.tex
Consistently use abbreviations GCS, MW and M31 for #1.

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy formation model used for the Auriga simulations
can produce a realistic globular cluster (GC) population. We compare statistics 
of GC candidate star particles in the Auriga haloes with catalogues of the Milky 
Way (MW) and Andromeda (M31) globular cluster populations. We find that the Auriga 
simulations do produce sufficient stellar mass for GC candidates at radii and 
metallicities that are typical for the MW GC system (GCS), although we observe a 
varying mass-ratio for different galactocentric radius-metallicity 
($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates relative to the 
observed mass in the MW and M31 GC systems.
This implies different values for the combined product of the bound cluster 
formation efficiency and the GC disruption rate. Furthermore we test whether any of the 
Auriga galaxies has a metallicity and radial distribution that is consistent with 
the MW or M31 GCS. For any one of the Auriga haloes we reject the null hypothesis
that the observed and simulated metallicities of GCs (GC candidates) are drawn
from the same distribution at $\geq98.32$~\% confidence level, for the GCS of 
the MW and M31. The same holds true for the distribution of $R_{\text{gal}}$.
Overall, the Auriga simulations produce GC candidates with higher metallicities 
than the MW and M31 GCS and at larger radii. This implies that the bound cluster
formation efficiency would have to decrease with increasing metallicity for the 
Auriga GC candidates to be consistent with the MW GCS, if GC disruption is equally 
efficient regardless of metallicity. In addition, the number of GCs relative to
field stars would have to be smaller for higher metallicity star particles at
large radii than for those with lower metallicity at smaller radii, assuming GC 
disruption is more efficient in the inner regions of the Galaxy.
\end{abstract}

@@

\section{Introduction}
Globular clusters (GC)s are old, bright, and ubiquitous. Various properties of
GC systems show correlations with their host galaxies. GC systems are believed to
retain information about the galactic (gas) conditions at their times of formation.
Thus they could offer a unique insight into the (chemodynamical) evolution of their 
parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
is adequately understood. However, despite decades of research (the extensive 
literature on GCs is summarised in several books and review articles, e.g.~\citealt{
1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 2006ARA&A..44..193B, 
2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}), consensus on an 
exhaustive picture of the formation of GCs is yet to be reached.

@@

Yet another hypothesis is that star cluster formation is triggered by major 
gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
which is naturally expected within the framework of hierarchical assembly. One
testable prediction of this scenario is the formation of young clusters in
interacting and merging galaxies, which has been observed and are found to show 
remarkable similarities with GCs in the Milky Way \citep[e.g.][]{
1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
produces star clusters that could be globular progenitors \citep{
2019arXiv190509840L}.

As for the formation timeline, the scenarios (and flavours thereof) of \citet{
1985ApJ...298...18F} and \citet{1992ApJ...384...50A} are intertwined because
accretion and mergers continuously occurs during the hierarchical build-up of
galaxies. Various (other) hierarchical formation channels thus combine different
aspects of the aforementioned paradigms, such as GC formation in (small) galactic
disks before they are accreted onto an assembling galaxy \citep[e.g.][]{
2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B, 2003egcs.conf..224G}. 
We refer to \citet{2001astro.ph..8034G} for a scoreboard of GC formation models 
compared to observations of the Milky Way globular cluster system.

@@

In this work we use state of the art simulations that produce realistic spiral 
galaxies (Milky Way analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GC system 
similar to the Milky Way and/or Andromeda globular cluster systems. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Sec.~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, 
radial, and metallicity-radial distributions that are consistent with the MW 
and/or M31 GC systems, and whether the model produces enough stellar mass with
the right properties to allow for formation efficiencies lower than unity and
the expected (dynamical) mass loss over the cluster lifetime (not modelled 
explicitly in this study).

The plan of the paper is as follows. We summarise the relevant characteristics 
of the Auriga simulations in section~\ref{sec:auriga}, followed by a summary of 
the observations of the Milky Way (MW) and Andromeda globular cluster system (GCS)
in section~\ref{sec:observations} that we use to compare our simulations to in
section~\ref{sec:results}. We discuss our findings in section~\ref{sec:discussion}
to come to our conclusions in section~\ref{sec:conclusions}.

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citepalias{2017MNRAS.467..179G}, a suite of 
high-resolution cosmological zoom simulations. The Milky Way-mass
selected initial conditions were selected from the \mbox{\textsc{eagle}} DM only 
box, see \citetalias{2017MNRAS.467..179G} for details. The simulations are performed with the \textsc{arepo} 
code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} that solves the 
magnetohydrodynamical equations on a moving mesh.

@@

\section{Observational data}
\label{sec:observations}
We describe the observations of the MW GCS in Sec.~\ref{sec:milkyway},
and of the Andromeda (M31) GCS in Sec.~\ref{sec:andromeda}

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the Milky Way globular cluster system that contains properties of 157 GCs. 
The authors initially estimated the number of GCs in the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GCs
are claimed to have been discovered by various authors. The total number of GCs
in the MW might add up to 216 with recent estimates now anticipating an additional 
thirty GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
50-70\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $R_{\text{gal}}=\sqrt{(X-R_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
magnitude in the V~band, $M_V$. We use the V~band magnitude to calculate 
mass-estimates by assuming $M_{V,\odot}=4.83$ and a mass to light ratio 
$M/L_V = 1.7$~M/L$_{\odot}$, the mean for MW clusters \citep{2005ApJS..161..304M}. 
We supplement the catalogue with age-estimates from isochrone fits to stars near 
the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.

% \citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
% available data, presented in their CatClu catalog. Amongst 10978 star clusters
% and alike objects in the Milky Way, the catalog contains 200 GCs and 94 GC
% candidates. The CatClu catalog contains reference papers, positions, distances,
% and total absolute V magnitude. Therefore we rely on the H96e10 dataset.

\subsection{Andromeda}
\label{sec:andromeda}
The fifth revision of the revised Bologna catalogue (RBC~5, last updated
August, 2012) is the latest edition of three decades of systematically
collecting integrated properties of the globular cluster system of the
Andromeda galaxy \citep[][and references therein]{2004A&A...416..917G}. One
contribution to RBC~5 is the work by \citet[][hereafter C11]{2011AJ....141...61C},
subsequently updated by \citet[][hereafter CR16]{2016ApJ...824...42C}.

C11 and CR16 present a uniform set of spectroscopic observations calibrated
on the Milky Way GCS of the inner $1.6^\circ~({\sim}21)$~kpc that
is believed to be 94\% complete. GCs in the outer stellar halo, up to
$R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, but see also
\citet{2014MNRAS.442.2929V} and \citet{2019MNRAS.484.1756M}. H14 presents the
discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
incorporated in the latest public release\footnote{Last revised 23 Sep 2015, see
\url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 dataset, further revised by CR16. We use CR16 because it is the most
recent aggregated dataset of M31's GCS that contains properties of interest
for our study and it includes GCs in the inner region and in the outer halo. The
relevant fields in the CR16 dataset that we use are the age, metallicity, and the
mass-estimate\footnote{The authors assumed $M/L_V = 2$ independent of [Fe/H]}.
Radii are calculated from RA and DEC, further discussed in Sec.~\ref{sec:Rgc}.

\subsection{Age-estimates}
The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
in CR16. The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCS's are not statistically consistent. Moreover, the Milky Way appears 
to host a globular cluster system that is somewhat older than the Andromeda galaxy,
which is somewhat surprising given that M31 is generally considered to be earlier
type than the MW meaning that an older stellar population would be naively expected.
However, we do caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

@@

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that few age-estimates are available 
for the innermost ($<1$~kpc) GCs, and none for those beyond roughly twenty
kpc (the halo GCs). We compare both distributions of the full data set (solid 
lines) and find that the Milky Way has more GCs in the range $1-4$~kpc than M31
(when accounting for the larger number of total GCs in M31). Interestingly, both
distributions show a similar trend for $R_{\text{gal}} > 4$~kpc and host a 
subpopulation of halo GCs. However, the two radial distributions are not statistically
consistent with being drawn from the same underlying distribution due to substantial 
differences at intermediate radii.

@@

\subsection{Total GC mass in metallicity-radial space} \label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. 
The observations indicate that
no GCs with high metallicities are to be expected at large radii (the three bins
in the upper right corner, both for MW and M31), and relatively few GCs at large
radii in general ($R_{\text{gal}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
([Fe/H]$ > -1$) GCs in each radial bin in comparison to the MW GCSs than what
would be expected when accounting for the fact that Andromeda hosts a larger GC 
system than the MW. Finally, given that both marginalized (i.e. the metallicity 
and radial) distributions are not statistically consistent, we find that the 
two-dimensional distributions are also not consistent. More generally, the GC
system of the MW differs significantly from that of M31. We compare these 
observations to the Auriga simulations later on in Sec.~\ref{sec:results_FeHRgc}.

@@

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the model implemented in Auriga produces metallicity 
distributions consistent with the MW and M31 GC systems, and whether
the simulations generate sufficient total mass at metallicities typical for the
MW and M31 GCS's. To visually inspect the former we show the normalized metallicity 
distribution of three specific Auriga galaxies in Figure~\ref{fig:Au4-10and21_FeH}
in comparison to the MW and M31 [Fe/H] distributions.

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21}.png}
    \caption{
        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
        purple (magenta) line shows the GC system of the MW (M31), and we 
        indicate the mean value with an arrow at the bottom of the x-axis. We
        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
        the mean and dispersion from \citep{Harris2001}.
        \emph{Other panels}: three selected Auriga haloes as indicated in the 
        upper right corner. In each of these three panels we show the GG 
        candicates in green, and use a green dotted line for all star particles. 
        We split the GC candidates up into two subpopulations, those that have 
        formed {\it in~situ} (blue), and those that have been accreted (red).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We show the age-selected GC candidates as well as the 
accreted and {\it in~situ} subsets. The top half of the left figure shows the MW 
and M31 GC systems, where we overplot a double Gaussian for the MW GCS by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep{Harris2001}.

We find that the age cut, on average, lowers the mean metallicity [Fe/H] from 
$0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
metallicities than the {\it in~situ} subset with differences of roughly
${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
seen in \mbox{Au4-21}, while a slightly larger difference of ${\sim}0.5$~dex is 
seen for \mbox{Au4-10} (as plotted), \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} 
and \mbox{Au4-22}. However, this trend is reversed for \mbox{Au4-1} and \mbox{Au4-4} 
for which the {\it in~situ} subset has a lower mean metallicity instead. 
\mbox{Au4-1} is undergoing a major merger at redshift zero and we find 
$\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} (accreted) GC candidates, 
although the former consists of only $1019$ particles ($1.3$\% of all GC 
candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
only ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared to 
{\it in~situ} fractions of ${40-80}$\% for other haloes). We note that \mbox{Au4-4}
has undergone a major merger around 2~Gyr lookback time, which is probably why
the accreted population is more metal rich. After inspection of the same figure 
for every one of the thirty Auriga L4 haloes we find that the simulations produce
(sub)populations of GC candidates that are more metal-rich than the MW and M31 GC 
systems. Moreover, none of the simulations has a (total) population of GC 
candidates with a bimodal metallicity distribution.

@@

We notice that the {\it in~situ} GC candidates are more centrally distributed, 
whereas the accreted subsets have a larger radial extent. This 
is not surprising because the classification of {\it in~situ} requires star particles 
to have formed within the virial radius, thus they could naturally be expected 
to end up at small galactocentric radii. Accreted star particles, on the other 
hand, have formed in another (sub)halo beyond the virial radius, thus, they would 
first have to migrate inwards in order to populate the innermost radii. Moreover,
we find that the simulations have a wider dispersion in $\log(R_{\text{gal}})$ than
the MW GCS, while the dispersion of M31 seems to lie within the range of dispersions
found in the Auriga galaxies. Furthermore, the mean of the MW GCS lies roughly 
within the range of values produced by the Auriga simulations, whereas the mean 
of M31 is somewhat larger and slightly closer to typical mean values of the 
accreted GC candidates in the Auriga simulations. The larger radial extent 
of the M31 GCS is generally believed to hint at a more accretion-dominated origin 
of the GCS, and may reflect a richer accretion history of M31 in comparison 
to the Milky Way.

>>>>

% Abstract of the paper
\begin{abstract}
We investigate whether the galaxy and star formation model used for the Auriga simulations
can produce a realistic globular cluster (GC) population. We compare statistics 
of GC candidate star particles in the Auriga haloes with catalogues of the Milky 
Way (MW) and Andromeda (M31) globular cluster populations. We find that the Auriga 
simulations do produce sufficient stellar mass for GC candidates at radii and 
metallicities that are typical for the MW GC system (GCS), although we observe a 
varying mass-ratio for different galactocentric radius-metallicity 
($R_{\text{gal}}$-[Fe/H]) bins of simulated GC candidates relative to the 
observed mass in the MW and M31 GC systems.
This implies different values for the combined product of the bound cluster 
formation efficiency and the GC disruption rate. Furthermore we test whether any of the 
Auriga galaxies has a metallicity and radial distribution that is consistent with 
the MW or M31 GCS. For any one of the Auriga haloes we reject the null hypothesis
that the observed and simulated metallicities of GCs (GC candidates) are drawn
from the same distribution at $\geq98.32$~\% confidence level, for the GCS of 
the MW and M31. The same holds true for the distribution of $R_{\text{gal}}$.
Overall, the Auriga simulations produce GC candidates with higher metallicities 
than the MW and M31 GCS and at larger radii. This implies that the bound cluster
formation efficiency would have to decrease with increasing metallicity for the 
Auriga GC candidates to be consistent with the MW GCS, if GC disruption is equally 
efficient regardless of metallicity. In addition, the number of GCs relative to
field stars would have to be smaller for higher metallicity star particles at
large radii than for those with lower metallicity at smaller radii, assuming GC 
disruption is more efficient in the inner regions of the Galaxy.
\end{abstract}

@@

\section{Introduction}
Globular star clusters (GC)s are old, bright, and ubiquitous. Various properties of
GC systems (GCS) show correlations with their host galaxies. GCSs are believed to
retain information about the galactic (gas) conditions at their times of formation.
Thus they could offer a unique insight into the (chemodynamical) evolution of their 
parent galaxies, if the formation and evolution of GCs- and GC systems themselves 
is adequately understood. However, despite decades of research (the extensive 
literature on GCs is summarised in several books and review articles, e.g.~\citealt{
1991ARA&A..29..543H, Harris2001, 2004Natur.427...31W, 2006ARA&A..44..193B, 
2012A&ARv..20...50G, 2014CQGra..31x4006K, 2018RSPSA.47470616F}), consensus on an 
exhaustive picture of the formation of GCs is yet to be reached.

@@

Yet another hypothesis is that star cluster formation is triggered by major 
gas-rich (spiral) galaxy mergers \citep{1987nngp.proc...18S, 1992ApJ...384...50A},
which is naturally expected within the framework of hierarchical assembly. One
testable prediction of this scenario is the formation of young clusters in
interacting and merging galaxies, which has been observed and are found to show 
remarkable similarities with GCs in the MW \citep[e.g.][]{
1995AJ....109..960W, 1996AJ....112..416H, 1999AJ....118..752Z, 1999AJ....118.1551W}.
Moreover, modelling efforts of this framework yield GC (sub)populations consistent 
with various observables \citep[e.g.][]{2010ApJ...718.1266M, 2018MNRAS.480.2343C}, 
and the recent numerical simulation of an isolated dwarf-dwarf merger executed at 
very high resolution (baryonic mass $m_b \sim$~4M\Sun; softening $\epsilon = 0.1$~pc) 
produces star clusters that could be globular progenitors \citep{
2019arXiv190509840L}.

As for the formation timeline, the scenarios (and flavours thereof) of \citet{
1985ApJ...298...18F} and \citet{1992ApJ...384...50A} are intertwined because
accretion and mergers continuously occurs during the hierarchical build-up of
galaxies. Various (other) hierarchical formation channels thus combine different
aspects of the aforementioned paradigms, such as GC formation in (small) galactic
disks before they are accreted onto an assembling galaxy \citep[e.g.][]{
2000ApJ...533..869C, 2002ApJ...567..853C, 2002MNRAS.333..383B, 2003egcs.conf..224G}. 
We refer to \citet{2001astro.ph..8034G} for a scoreboard of GC formation models 
compared to observations of the MW GCSs.

@@

In this work we use state of the art simulations that produce realistic spiral 
galaxies (MW analogues) at redshift zero for which several global properties 
are consistent with the observations. The question thus naturally arises whether 
the star formation histories of the simulations give rise to a GCS similar to 
the MW and/or M31 GCSs. In particular, 
we use the Auriga simulations \citep[][hereafter G17]{2017MNRAS.467..179G}, 
further described in Sec.~\ref{sec:auriga}. We investigate whether the star 
formation model implemented produces metallicity, 
radial, and metallicity-radial distributions that are consistent with the MW 
and/or M31 GCSs, and whether the model produces enough stellar mass with
the right properties to allow for formation efficiencies lower than unity and
the expected (dynamical) mass loss over the cluster lifetime (not modelled 
explicitly in this study).

The plan of the paper is as follows. We summarise the relevant characteristics 
of the Auriga simulations in section~\ref{sec:auriga}, followed by a summary of 
the observations of the MW and M31 GCSs
in section~\ref{sec:observations} that we use to compare our simulations to in
section~\ref{sec:results}. We discuss our findings in section~\ref{sec:discussion}
to come to our conclusions in section~\ref{sec:conclusions}.

\section{The Auriga simulations}
\label{sec:auriga}
We use the Auriga simulations \citepalias{2017MNRAS.467..179G}, a suite of 
high-resolution cosmological zoom simulations of MW analogues. The MW-mass
selected initial conditions were selected from the \mbox{\textsc{eagle}} DM only 
box, see \citetalias{2017MNRAS.467..179G} for details. The simulations are 
performed with the \textsc{arepo} code \citep{2010MNRAS.401..791S, 2016MNRAS.455.1134P} 
that solves the magnetohydrodynamical equations on a moving mesh.

@@

\section{Observational data}
\label{sec:observations}
We describe the observations of the MW GCS in Sec.~\ref{sec:milkyway},
and of the M31 GCS in Sec.~\ref{sec:andromeda}

\subsection{Milky Way}
\label{sec:milkyway}
\citet[][2010 edition; hereafter H96e10]{1996AJ....112.1487H} provides a
catalogue\footnote{See \url{https://www.physics.mcmaster.ca/Fac_Harris/mwgc.dat}}
of the MW GCS that contains properties of 157 GCs. 
The authors initially estimated the number of GCs in the MW GCS to be 180~$\pm$~10,
thus, their catalogue to be ${\sim}$85\% complete. However, an additional 59 GCs
are claimed to have been discovered by various authors. The total number of GCs
in the MW might add up to 216 with recent estimates now anticipating an additional 
thirty GCs yet to be discovered \citep[e.g.][and references therein]{2018ApJ...863L..38R}.
We still use data from the Harris catalogue, but caution that it may (only) be
50-70\% complete. Specifically, the relevant data fields that we use from H96e10
are the metallicity [Fe/H], the Galactic distance components $X$, $Y$, and $Z$ (in
kpc)\footnote{In a Sun-centered coordinate system: $X$ points toward Galactic
center, $Y$ in direction of Galactic rotation, and $Z$ toward the North Galactic
Pole. We calculate the galactocentric radius $R_{\text{gal}}=\sqrt{(X-R_\odot)^2
+ Y^2 + Z^2}$, assuming the solar radius $R_\odot=8$~kpc.}, and absolute
magnitude in the V~band, $M_V$. We use the V~band magnitude to calculate 
mass-estimates by assuming $M_{V,\odot}=4.83$ and a mass to light ratio 
$M/L_V = 1.7$~M/L$_{\odot}$, the mean for MW clusters \citep{2005ApJS..161..304M}. 
We supplement the catalogue with age-estimates from isochrone fits to stars near 
the main-sequence turnoff in 55 GCs \citep[][hereafter V13]{2013ApJ...775..134V}.

% \citet{2019AJ....157...12B} communicate the latest efforts to aggregate the
% available data, presented in their CatClu catalog. Amongst 10978 star clusters
% and alike objects in the MW, the catalog contains 200 GCs and 94 GC
% candidates. The CatClu catalog contains reference papers, positions, distances,
% and total absolute V magnitude. Therefore we rely on the H96e10 dataset.

\subsection{Andromeda}
\label{sec:andromeda}
The fifth revision of the revised Bologna catalogue (RBC~5, last updated
August, 2012) is the latest edition of three decades of systematically
collecting integrated properties of the GCS of M31 \citep[][and references therein]{2004A&A...416..917G}. One
contribution to RBC~5 is the work by \citet[][hereafter C11]{2011AJ....141...61C},
subsequently updated by \citet[][hereafter CR16]{2016ApJ...824...42C}.

C11 and CR16 present a uniform set of spectroscopic observations calibrated
on the MW GCS of the inner $1.6^\circ~({\sim}21)$~kpc that
is believed to be 94\% complete. GCs in the outer stellar halo, up to
$R_{\text{proj}}\sim150$~kpc, are observed in the Pan-Andromeda Archaeological
Survey \citep[PAndAS, ][hereafter H14]{2014MNRAS.442.2165H}, but see also
\citet{2014MNRAS.442.2929V} and \citet{2019MNRAS.484.1756M}. H14 presents the
discovery of 59 new GCs and publishes updates to RBC~5. The work of H14 is
incorporated in the latest public release\footnote{Last revised 23 Sep 2015, see
\url{https://www.cfa.harvard.edu/oir/eg/m31clusters/M31_Hectospec.html}}
of the C11 dataset, further revised by CR16. We use CR16 because it is the most
recent aggregated dataset of M31's GCS that contains properties of interest
for our study and it includes GCs in the inner region and in the outer halo. The
relevant fields in the CR16 dataset that we use are the age, metallicity, and the
mass-estimate\footnote{The authors assumed $M/L_V = 2$ independent of [Fe/H]}.
Radii are calculated from RA and DEC, further discussed in Sec.~\ref{sec:Rgc}.

\subsection{Age-estimates}
The top panel of Figure~\ref{fig:MW-M31-age-Rgc} shows a histogram of the age-estimates
of the $55$ MW GCs in V13 and $88$ GCs in M31 for which age-estimates are available
in CR16. The mean age of the MW GCs in this data set is $11.9 \pm 0.1$~Gyr and the 
dispersion is $0.8$~Gyr. Furthermore, only one of the 55 GC age-estimates is
below $10$~Gyr. The M31 GCS has a mean age of $11.0 \pm 0.2$~Gyr with a dispersion 
of $2.2$~Gyr, and $24$ GCs have age-estimates below $10$~Gyr with a minimum age 
of $4.8$~Gyr. Based on these data, we find that the age distributions of the MW 
and M31 GCSs are not statistically consistent. Moreover, the MW appears 
to host a GCS that is somewhat older than that of M31.
This is somewhat surprising given that M31 is generally considered to be earlier
type than the MW meaning that an older stellar population would be naively expected.
However, we do caution that both data sets are incomplete and the age 
measurements have large uncertainties (of $1-2$~Gyr). On the other hand, the 
magnitude of the uncertainty is insufficient to explain the low-age tail in M31.

@@

The solid lines show the distributions using all available data (because the
sky coordinates are known for each GC), while the subset for which age-estimates
are available is indicated using dotted lines. The latter shows a narrower range
of radii than the full data set: it appears that few age-estimates are available 
for the innermost ($<1$~kpc) GCs, and none for those beyond roughly twenty
kpc (the halo GCs). We compare both distributions of the full data set (solid 
lines) and find that the MW has more GCs in the range $1-4$~kpc than M31
(when accounting for the larger number of total GCs in M31). Interestingly, both
distributions show a similar trend for $R_{\text{gal}} > 4$~kpc and host a 
subpopulation of halo GCs. However, the two radial distributions are not statistically
consistent with being drawn from the same underlying distribution due to substantial 
differences at intermediate radii.

@@

\subsection{Total GC mass in metallicity-radial space} \label{sec:observations_FeHRgc}
We show the two-dimensional mass-weighted metallicity-radial distribution of the
MW (M31) GCS in the top (bottom) panel of Figure~\ref{fig:observations_FeHRgc}. 
The observations indicate that
no GCs with high metallicities are to be expected at large radii (the three bins
in the upper right corner, both for MW and M31), and relatively few GCs at large
radii in general ($R_{\text{gal}} > 30$~kpc; right column: $11$ GCs or 7.3\% in
the MW and $17$ or 4.6\% in M31). Moreover, the M31 hosts more metal-rich 
([Fe/H]$ > -1$) GCs in each radial bin in comparison to the MW GCSs than what
would be expected when accounting for the fact that M31 hosts a larger GCS
than the MW. Finally, given that both marginalized (i.e. the metallicity 
and radial) distributions are not statistically consistent, we find that the 
two-dimensional distributions are also not consistent. More generally, the GCS
of the MW differs significantly from that of M31. We compare these 
observations to the Auriga simulations later on in Sec.~\ref{sec:results_FeHRgc}.

@@

\subsection{Metallicity distribution}
\label{sec:results_FeH}
We investigate whether the model implemented in Auriga produces metallicity 
distributions consistent with the MW and M31 GCSs, and whether
the simulations generate sufficient total mass at metallicities typical for the
MW and M31 GCSs. To visually inspect the former we show the normalized metallicity 
distribution of three specific Auriga galaxies in Figure~\ref{fig:Au4-10and21_FeH}
in comparison to the MW and M31 [Fe/H] distributions.

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21}.png}
    \caption{
        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
        purple (magenta) line shows the GCSs of the MW (M31), and we 
        indicate the mean value with an arrow at the bottom of the x-axis. We
        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
        the mean and dispersion from \citep{Harris2001}.
        \emph{Other panels}: three selected Auriga haloes as indicated in the 
        upper right corner. In each of these three panels we show the GG 
        candicates in green, and use a green dotted line for all star particles. 
        We split the GC candidates up into two subpopulations, those that have 
        formed {\it in~situ} (blue), and those that have been accreted (red).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We show the age-selected GC candidates as well as the 
accreted and {\it in~situ} subsets. The top half of the left figure shows the MW 
and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep{Harris2001}.

We find that the age cut, on average, lowers the mean metallicity [Fe/H] from 
$0.0$ to $-0.6$. Furthermore, accreted GC candidates generally have lower mean 
metallicities than the {\it in~situ} subset with differences of roughly
${\sim}0.3$~dex for the majority of the simulation runs. This behaviour can be 
seen in \mbox{Au4-21}, while a slightly larger difference of ${\sim}0.5$~dex is 
seen for \mbox{Au4-10} (as plotted), \mbox{Au4-16}, \mbox{Au4-17}, \mbox{Au4-18} 
and \mbox{Au4-22}. However, this trend is reversed for \mbox{Au4-1} and \mbox{Au4-4} 
for which the {\it in~situ} subset has a lower mean metallicity instead. 
\mbox{Au4-1} is undergoing a major merger at redshift zero and we find 
$\mu = -1.51 \, ({-0.74})$ for the {\it in~situ} (accreted) GC candidates, 
although the former consists of only $1019$ particles ($1.3$\% of all GC 
candidates, and with a total mass of $5 \times 10^{7}$~M\Sun). For \mbox{Au4-4}, 
only ${10.8}$\% of the GC candidates is classified as {\it in~situ} (compared to 
{\it in~situ} fractions of ${40-80}$\% for other haloes). We note that \mbox{Au4-4}
has undergone a major merger around 2~Gyr lookback time, which is probably why
the accreted population is more metal rich. After inspection of the same figure 
for every one of the thirty Auriga L4 haloes we find that the simulations produce
(sub)populations of GC candidates that are more metal-rich than the MW and M31 GCSs.
Moreover, none of the simulations has a (total) population of GC 
candidates with a bimodal metallicity distribution.

@@

We notice that the {\it in~situ} GC candidates are more centrally distributed, 
whereas the accreted subsets have a larger radial extent. This 
is not surprising because the classification of {\it in~situ} requires star particles 
to have formed within the virial radius, thus they could naturally be expected 
to end up at small galactocentric radii. Accreted star particles, on the other 
hand, have formed in another (sub)halo beyond the virial radius, thus, they would 
first have to migrate inwards in order to populate the innermost radii. Moreover,
we find that the simulations have a wider dispersion in $\log(R_{\text{gal}})$ than
the MW GCS, while the dispersion of M31 seems to lie within the range of dispersions
found in the Auriga galaxies. Furthermore, the mean of the MW GCS lies roughly 
within the range of values produced by the Auriga simulations, whereas the mean 
of M31 is somewhat larger and slightly closer to typical mean values of the 
accreted GC candidates in the Auriga simulations. The larger radial extent 
of the M31 GCS is generally believed to hint at a more accretion-dominated origin 
of the GCS, and may reflect a richer accretion history of M31 in comparison 
to the MW.
